\section*{Q4}

The oracle translations tend to have better BLEU scores. The oracle outputs are intuitively better, but not without exceptions. Let's look at the first example in section \textit{Oracle} of table~\ref{translation_compare}.
  
The oracle translation, on top of from not omitting \textit{the residents}, accounts for the English distinction between \textit{house} and \textit{home}. However, the preferred preposition of \textit{the stairwell} was correctly chosen by the default reranker and not by the oracle.
Similarly in the second and third example, the oracle provides a more fluent translation, being able to create a fully formed sentence made up of complex clause types.

However, there are still many less-than-good translations. These occur inter alia when sentences have rare special characters (example five); Russian conventions for comparatives are retained, resulting in poorly-formed English sentences (example six); sentence is longer, with more complex clausal structure is (example seven).

Since the oracle's aim it to maximize BLEU by choosing from the provided top candidates, the above shortcomings likely reflect both the deficiencies of the decoder (and statistical models) used to produce the candidates and of BLEU as a metric of translation quality. Sometimes there are no good translations among the candidates, as for the sentence about 20 planes. In other cases, illustrated by example four in table~\ref{translation_compare}, even though the choice of the default reranker is clearly better, its BLUE score is lower.

%\begin{longtable}
%	\centering
	\begin{longtable}{||c|c||}
	\hline
	\textbf{Default} & \textbf{Flipped LM}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} "cold and inhuman": anders беринг\\breivik first publicly trial\vspace{.5\baselineskip}} &
	\parbox{7cm}{\vspace{.5\baselineskip} "cold and inhuman": anders fogh\\беринг breivik publicly appears before\\by the court for the first time"\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} after the summer the researchers\\wanted to learn more about\\these people.\vspace{.5\baselineskip}} &
	\parbox{7cm}{\vspace{.5\baselineskip} after summer of the tragedy\\the researchers want to learn\\more about the these people.\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} someone can use the ' language '\\when answering a question :\\" well... the truth... how do i know...\\as far as i know."\vspace{.5\baselineskip}} &
	\parbox{7cm}{\vspace{.5\baselineskip} somebody can use the ' qualification\\language ', when responds to\\a difficult question :" well...\\the truth... as far as i know...\\as far as i know."\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} " this paper tiger, the army barracks,\\buildings and bombs without enough\\trained soldiers, to accomplish the\\mission," panetta said in his introductory\\remarks at the pentagon.\vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} "it 's a paper tiger, the army with the\\barracks, buildings and bombs without\\enough trained soldiers, who can\\accomplish the mission,"panetta said in\\ their introductory remarks in the pentagon.\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} you need to keep in mind 5,000\\these concepts, ideas - them all together.\vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} you need to keep in the head\\of the 5,000 of ideas - these concepts,\\combining them all together...\vspace{.5\baselineskip}}\\
	\hline
	\textbf{Default} & \textbf{Oracle}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} the police statement reported that\\the home noticed smoke in\\the apartment stairwell and... \vspace{.5\baselineskip}} &
	\parbox{7cm}{\vspace{.5\baselineskip} police in a statement reported that\\residents of the house noticed\\smoke on the apartment stairwell and... \vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} bella in the fourth finally able\\to marry her lover\vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} bella in a fourth part finally\\manages to marry her beloved.\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} before, if you want to interview\\people from the british national party,\\would be very difficult to\vspace{.5\baselineskip}} &
	\parbox{7cm}{\vspace{.5\baselineskip} previously, if you wanted to interview\\people from the british national party,\\it would be very difficult\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} two 19 - year - old tried to help\\young people, but were\\immediately beaten by four men. \vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} two 19 - year - olds young people\\trying to help, but were\\just beaten by the four men. \vspace{.5\baselineskip}}\\
	\hline
	 & \parbox{7cm}{\vspace{.5\baselineskip}including an option to buy 20 more\\planes, total volume, in fact,\\the \$26 billion.\vspace{.5\baselineskip}}\\
	 \hline
	 & \parbox{7cm}{\vspace{.5\baselineskip}but residents complaining of the dirt\\and noise, in many communities\\is becoming more and more.\vspace{.5\baselineskip}}\\
	 \hline
	 & \parbox{7cm}{\vspace{.5\baselineskip}all four birds used the wire to make\\and used hooks hooks, to\\a bucket for pen and pull\\him out of the cylinder\vspace{.5\baselineskip}}\\
	\hline
	\textbf{Deafult} & \textbf{Best parameters}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} the training took place late on\\monday on...\vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} the latest training took place late\\on monday on...\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} will new measures supported the council\\on foreign affairs or расколют lawmakers\\as the june bill ?...\vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} whether the new measures will receive full\\support of the council on foreign affairs\\or расколют legis...\vspace{.5\baselineskip}}\\
	\hline
	\parbox{7cm}{\vspace{.5\baselineskip} facebook also draws all kinds of data\\about its users. \vspace{.5\baselineskip}}&
	\parbox{7cm}{\vspace{.5\baselineskip} facebook also constantly pulls all sorts\\of data about its users.\vspace{.5\baselineskip}}\\
	\hline
	\caption{Comparison of outputs of the reranker with different configurations.}\label{translation_compare}
	\end{longtable}
	%\caption{Comparison of outputs of the reranker with different configurations.}\label{translation_compare}
%\end{longtable}
